%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {2024-Now} % Year
    {Junior postdoctoral fellow FWO} % Position
    {AIMS lab, VUB} % Institution
  \cvskillextended
    {}
    {Postdoctoral researcher funded by a personal junior postdoctoral fellowship. Title: Leveraging recent advances in explainable AI to decode cognitive functioning from T1/FLAIR weighted MR images in MS - An international federated learning approach (12A6U25N). More info: See 'Awards' tab.} % Description
    {}


%---------------------------------------------------------
  \cvskill
    {2019-2024} % Year
    {PhD Student (VLAIO Baekeland)} % Position
    {Industrial doctorate. AIMS lab (VUB) and icometrix NV (Leuven)} % Institution
  \cvskillextended
    {}
    {Title: Structural brain damage and cognition in MS: an AI approach (HBC.2019.2579). See 'Education' and 'Awards' for more detail.} % Description
    {}


%---------------------------------------------------------
  \cvskill
    {2018-2019} % Year
    {Research assistant Prof. Guy Nagels} % Position
    {AIMS lab, VUB} % Institution
  \cvskillextended
    {}
    {Initial lab experience working on various projects, including a project on NMSC Melsbroek rehabilitation data, resulting in a paper in the Journal of Central Nervous System Disease, and continuing the Cochrane update.} % Description
    {}


%---------------------------------------------------------
  \cvskill
    {2018} % Year
    {Physical therapist} % Position
    {National Multiple Sclerosis Center Melsbroek} % Institution
  \cvskillextended
    {}
    {Rehabilitation of patients with multiple sclerosis.} % Description
    {}


%---------------------------------------------------------
  \cvskill
    {2018} % Year
    {Research assistant Prof. Geert Verheyden} % Position
    {Dept. Rehabilitation Sciences, KU Leuven} % Institution
  \cvskillextended
    {}
    {Updating the 2013 Cochrane review of Prof. Verheyden, resulting in a paper in 2019.} % Description
    {}


%---------------------------------------------------------
  \cvskill
    {2017} % Year
    {Physical therapist} % Position
    {GIRA Campus Pellenberg, UZ Leuven} % Institution
  \cvskillextended
    {}
    {Geriatric intensive rehabilitation, mainly of patients having suffered a stroke.} % Description
    {}


\end{cvskills}