%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}

\begin{cvpubs}

    \cvpub{\textbf{Denissen S}, Laton J, Grothe M, Vaneckova M, Uher T, Kudrna M, Horáková D, Baijot J, Penner I-K, Kirsch M, Motýl J, De Vos M, Chén OY, Van Schependom J and Nagels G 2026. Real-world federated learning for brain imaging scientists. Frontiers in Digital Health 8:1691088.\hfill \textbf{IF: 3.8, Q1 2024}}

    \cvpub{Xinguang Wang, Nguyen Linh Trung, Oliver Y. Chen, Jeroen Van Schependom, Stijn Denissen and Guy Nagels 2026. PDD-FANs: Personalized Decentralized Federated Adversarial Networks with Defense Mechanism in Non-IID Setting. IEEE TrustCom 2025 (Conference) .}

    \cvpub{Sosa A, O’Neill KA, Billiet T, Chen J, Couvreur L, \textbf{Denissen S}, Lustberg M, Pehel S, Ribbens A and Krupp L 2025. Incorporating measures of cognitive processing speed and brain volume in clinical management of pediatric onset MS. Pediatric Neurology .\hfill \textbf{IF: 2.1,  2024}}

    \cvpub{Trinh Ngoc Huynh, Nguyen Duc Kien, Nguyen Hai Anh, Dinh Tran Hiep, Manuela Vaneckova, Tomas Uher, Jeroen Van Schependom, Stijn Denissen, Tran Quoc Long, Nguyen Linh Trung and Guy Nagels 2025. Latent Representation Learning from 3D Brain MRI for Interpretable Prediction in Multiple Sclerosis. arXiv preprint arXiv:2510.00051.}

    \cvpub{\textbf{Denissen S}*, Van Laethem D*, Baijot J, Costers L, Descamps A, Van Remoortel A, Van Merhaegen-Wieleman A, D’hooghe M, D'Haeseleer M, Smeets D, Sima DM, Van Schependom J and Nagels G 2025. A New Smartphone-Based Cognitive Screening Battery for Multiple Sclerosis (icognition): Validation Study. Journal of Medical Internet Research 27, e53503.\hfill \textbf{IF: 6.0,  2024}}

    \cvpub{De Keersmaecker E, Guida S, \textbf{Denissen S}, Dewolf L, Nagels G, Jansen B, Beckwée D and Swinnen E 2025. Virtual reality for multiple sclerosis rehabilitation. Cochrane Database of Systematic Reviews (1).\hfill \textbf{IF: 9.4,  2024}}

    \cvpub{Wittens MMJ*, \textbf{Denissen S}*, Sima DM, ..., Engelborghs S 2024. Brain age as a biomarker for pathological versus healthy ageing–a REMEMBER study. Alzheimer's research \& therapy 16.1 (2024): 128.\hfill \textbf{IF: 7.6,  2024}}

    \cvpub{Van Laethem D*, \textbf{Denissen S}*, Costers L, Descamps A, Baijot J, Van Remoortel A, Van Merhaegen-Wieleman A, D’hooghe M, D'Haeseleer M, Smeets D, Sima DM, Van Schependom J and Nagels G 2024. The Finger Dexterity Test: Validation study of a smartphone-based manual dexterity assessment. Multiple Sclerosis Journal 30(1), 121-130.\hfill \textbf{IF: 5.0,  2024}}

    \cvpub{\textbf{Denissen S}, Van Schependom J, Nagels G 2023. Medical diagnosis and a new kid in town: AI. Book chapter in VUB book 'A question of truth' .}

    \cvpub{Thijs L, Voets E, \textbf{Denissen S}, Mehrholz J, Elsner B, Lemmens R and Verheyden G 2023. Trunk training for improving activities in people with stroke. Stroke 54(9), e427-e428.\hfill \textbf{IF: 7.9,  2023}}

    \cvpub{Thijs L, Voets E, \textbf{Denissen S}, Mehrholz J, Elsner B, Lemmens R and Verheyden G 2023. Trunk training for improving activities in people with stroke. Cochrane Database of Systematic Reviews (3).\hfill \textbf{IF: 8.8,  2023}}

    \cvpub{Baijot J, Van Laethem D, \textbf{Denissen S}, Costers L, Cambron M, D’Haeseleer M, D’hooghe MB, Vanbinst A, De Mey J, Nagels G and Van Schependom J 2022. Radial diffusivity reflects general decline rather than specific cognitive deterioration in multiple sclerosis. Scientific Reports 12(1), 21771.\hfill \textbf{IF: 4.6,  2022}}

    \cvpub{\textbf{Denissen S} and Nagels G 2022. Artificial intelligence will change MS care within the next 10 years: Yes. Multiple Sclerosis Journal 28(14): e53503.\hfill \textbf{IF: 5.8,  2022}}

    \cvpub{\textbf{Denissen S}, Engemann DA, De Cock A, Costers L, Baijot J, Laton J, Penner I-K, Grothe M, Kirsch M, D'hooghe MB, D'Haeseleer M, Dive D, De Mey J, Van Schependom J, Sima DM and Nagels G 2022. Brain age as a surrogate marker for cognitive performance in multiple sclerosis. European journal of neurology 29(10): 3039-3049.\hfill \textbf{IF: 5.1,  2022}}

    \cvpub{\textbf{Denissen S}, Chen OY, De Mey J, De Vos M, Van Schependom J, Sima DM and Nagels, G 2021. Towards multimodal machine learning prediction of individual cognitive evolution in multiple sclerosis. Journal of personalized medicine 11(12), 1349.\hfill \textbf{IF: 3.508,  2021}}

    \cvpub{Baijot J*, \textbf{Denissen S}*, Costers L, Gielen J, Cambron M, D'Haeseleer M, D'hooghe MB, Vanbinst A, De Mey J, Nagels G and Van Schependom J 2021. Signal quality as Achilles’ heel of graph theory in functional magnetic resonance imaging in multiple sclerosis. Scientific Reports 11(1), 7376.\hfill \textbf{IF: 4.997,  2021}}

    \cvpub{\textbf{Denissen S}, Staring W, Kunkel D, Pickering RM, Lennon S, Geurts ACH, Weerdesteyn V and Verheyden GS 2020. Interventions for preventing falls in people after stroke. Stroke 51 (3), e47-e48.\hfill \textbf{IF: 7.914,  2020}}

    \cvpub{\textbf{Denissen S}, De Cock A, Meurrens T, Vleugels L, Van Remoortel A, Gebara B, D’Haeseleer M, D’Hooghe MB, Van Schependom J, and Nagels G 2019. The Impact of Cognitive Dysfunction on Locomotor Rehabilitation Potential in Multiple Sclerosis. Journal of central nervous system disease 11, 1179573519884041.}

    \cvpub{\textbf{Denissen S}, Staring W, Kunkel D, Pickering RM, Lennon S, Geurts ACH, Weerdesteyn V and Verheyden GS 2019. Interventions for preventing falls in people after stroke. Cochrane database of systematic reviews (10).\hfill \textbf{IF: 7.89,  2019}}

\end{cvpubs}

\begin{flushright}
    \vspace{0.5cm}
    * indicates joint first authorship.
\end{flushright}