%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Science communication and media}

Over the years, I experimented with different forms of science communication,  tailored for different audiences including physiotherapists, patients with MS,  and even children. My idea to turn a paper into a song was particularly well received;  SciMingo asked me to perform live at the final of the Flemish Thesis Prize  at the Brussels city hall. Finally, I poured my PhD into a 3 minute song,  performing it live when I received the ‘PhD of The Year’ award.


\begin{cvhonors}

%---------------------------------------------------------
  \cvhonor
    {\href{https://aiptit3mtcompetition.pages.dev/}{3 minute thesis competition Vietnam}} % Event/Organization
    {Jury member for a national competition on science communication among engineering students. The challenge: to explain their research in 3 minutes with a single slide.} % Position/Description
    {Event} % Location/Type
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://ertsberg.be/boek/vergeet-dementie/}{Vergeet Dementie}} % Event/Organization
    {I contributed to the vulgarising book 'Vergeet Dementie' by authors Ms. Ceuleers and Prof. Engelborghs. I was interviewed by Ms. Ceuleers about the concept of 'brain age', and provided a layman summary for their book.} % Position/Description
    {Event} % Location/Type
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.despecialist.eu/nl/nieuws/nieuwe-vub-app-moet-helpen-bij-snellere-screening-multiple-sclerose.html}{De Specialist}} % Event/Organization
    {Interview on smartphone symptom screening together with Dr. Delphine Van Laethem (also in other media channels)} % Position/Description
    {Interview} % Location/Type
    {2025} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://apps.congrex.com/ectrims2024/en-GB/pag/presentation/360049}{LACTRIMS interview}} % Event/Organization
    {Interview by Dr. Lorna Galleguillos on my talk entitled 'What artificial intelligence tools are ready for MS clinical practice' during the educational session on 'Clinical implications of digital monitoring and artificial intelligence in MS and related disorders' at ECTRIMS 2024 in Copenhagen} % Position/Description
    {Interview} % Location/Type
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.youtube.com/watch?v=g00caqB9VlA}{Award ceremony 'PhD of The Year'}} % Event/Organization
    {Live performance of my PhD in a 3-minute song, in synchrony with my 'a paper in a song' initiative.} % Position/Description
    {Live Performance} % Location/Type
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.nieuwsblad.be/natuur-en-wetenschap/onze-man-gaat-onder-de-mri-scanner-en-laat-zijn-hersenleeftijd-bepalen-we-hebben-je-binnenste-gezien/55321745.html}{Het Nieuwsblad}} % Event/Organization
    {Interview on brain age} % Position/Description
    {Interview} % Location/Type
    {2024} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.youtube.com/watch?v=R6r3SouhEjE}{VUB PhD day}} % Event/Organization
    {Live performance 'A paper in a song'} % Position/Description
    {Live Performance} % Location/Type
    {2023} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://belux.edmo.eu/event/book-launch-a-question-of-truth/}{Book presentation 'A question of truth'}} % Event/Organization
    {Interview in the Brussels city hall together with my promoter Prof. Guy Nagels. We discussed our chapter contribution on medical diagnosis and AI.} % Position/Description
    {Interview} % Location/Type
    {2023} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://x.com/SciMingo/status/1605284188780957698}{Award ceremony Flemish Thesis Prize (SciMingo)}} % Event/Organization
    {Live performance 'A paper in a song'} % Position/Description
    {Live Performance} % Location/Type
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://issuu.com/kngfdefysiotherapeut/docs/fysiopraxis-_mei2022}{KNGF Fysiopraxis}} % Event/Organization
    {Vulgarising article about our Cochrane review on interventions to prevent falls post-stroke. Title: 'Oefentherapie voorkomt vallen na een CVA'.} % Position/Description
    {Article} % Location/Type
    {2022} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://vubkinderuniversiteit.be/ku21-workshop-hoe-oud-is-mijn-brein/}{Children's university VUB}} % Event/Organization
    {Title of the workshop I presented to primary school childeren: 'How old is my brain?'. In this workshop, I converted my PhD work in a comprehensible framework for young children. Together, we explored how AI can measure brain structures, and how we can use it to predict the age of my brain.} % Position/Description
    {Event} % Location/Type
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.youtube.com/@apaperinasong1222}{YouTube channel}} % Event/Organization
    {} % Position/Description
    {Website} % Location/Type
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://artsenkrant.pmg.be/nl/dossier/EAKbe2118W19_00}{Artsenkrant}} % Event/Organization
    {Interview about ACTRIMS 2021 presentation on brain age.} % Position/Description
    {Interview} % Location/Type
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.eoswetenschap.eu/technologie/hersenspinsels-een-editie-over-cognitie}{Wetenschap Brussel + EOS (Cognition)}} % Event/Organization
    {Blog about cognition, together with Dr. Delphine Van Laethem. Title: 'Hersenspinsels: een editie over cognitie'} % Position/Description
    {Article} % Location/Type
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.healio.com/news/neurology/20210225/brain-age-serves-as-sensitive-marker-for-information-processing-speed-in-ms}{Haelio Neurology}} % Event/Organization
    {Interview about ACTRIMS 2021 presentation on brain age} % Position/Description
    {Interview} % Location/Type
    {2021} % Date(s)

%---------------------------------------------------------
  \cvhonor
    {\href{https://www.eoswetenschap.eu/technologie/hersenspinsels-artificiele-intelligentie}{Wetenschap Brussel + EOS (AI)}} % Event/Organization
    {Blog about artificial intelligence.Title: 'Hersenspinsels: artificiële intelligentie'} % Position/Description
    {Article} % Location/Type
    {2020} % Date(s)

\end{cvhonors}

 \hfill \textit{Note: Please click text in bold for more info if available.}